StreamReduce: A Data Stream Processor with MapReduce Parallelism

### 2012-05-15 paper/paper.tex
Incorporate edits from Martin
I had a couple of typos and redid section 5.1, 5.1.1, and 5.1.2.
Talked about the stability of the word count distribution and how
stability influences the effectiveness of a task killing framework

The most important piece Dynamic Knobs offers to the DSMS space is dynamic
\emph{peak load provisioning}. Their system can adjust downward the amount of resources,
machines, etc\. required for normal load and quickly adjust these levels back up to
handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
be used to create a DSMS that uses less resources in both the normal and peak load
states.

@@

\subsection{Precision and Recall}
For task killing to be an effective strategy in a top-k computation, the
distribution of words in the corpus must be able to sustain data loss. This is the case
if the distribution is long-tailed, but is not true if the distribution is uniform.

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-
tailed distribution. This graph has had stop words~\cite{stopwords} filtered out of it.}
\label{fig:wordDist}
\end{figure}

The distribution shown in Figure~\ref{fig:wordDist} is long-tailed. This implies that killing
tasks will impact the tail of the distribution more than the head.

\subsubsection{Precision}
Task killing should least impact the head of the word distribution.
Figure~\ref{fig:precision} shows that even with a task kill rate of~0.8 and a work level of~0.4,
meaning that the cluster only looks at 8\% of the words in the corpus, the results
are at least~80\% accurate. Increasing the work level, which increases the fidelity of
results emitted by workers, also increases the fidelity of the top~100 results.

@@

\subsubsection{Recall}
Recall in the tail of the distribution is most dependent on the work level of the word count
job.
Anything less than perfect computation of a datum leaves out words with a frequency of one.
Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
the same effect on recall as using low fidelity computation routines, so recall decreases as
the task kill rate does. Task killing dominates the impact of work level on recall as
demonstrated
by the two lines converging in Figure~\ref{fig:recall}.

>>>>

The most important piece Dynamic Knobs offers to the DSMS space is dynamic
\emph{peak load provisioning}. Their system can adjust downward the amount of resources,
machines, etc\@. required for normal load and quickly adjust these levels back up to
handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
be used to create a DSMS that uses less resources in both the normal and peak load
states.

@@

\subsection{Precision and Recall}
For task killing to be an effective strategy in a top-k computation,
the distribution of the top-k words must be stable. A stable distribution is one
that is not altered by adding an additional article to or removing the last
article from the corpus. Stable distributions are able to sustain the data lost in
an approach like task killing.

Every data set has some base level of noise in it due to such things as how the data is
sampled. StreamReduce introduces another source of noise by discarding data and
substituting computation algorithms. If the noise introduced by StreamReduce is less than
the data set's sensitivity to noise, the top-k words remain stable.

For example, if the distribution of words in the test corpus is close to uniform, the top-k
words are bunched together and any perturbations in the tested data, for example, discarding an
article that contains instances of the real top-k words, will affect the fidelity of the
reported top-k.

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a
long-tailed distribution. This graph has had stop words~\cite{stopwords} filtered out of it.}
\label{fig:wordDist}
\end{figure}

The distribution of words in the Wikipeida data set is
shown in Figure~\ref{fig:wordDist}. The distribution is long-tailed, which is a first step
in verifying that this data set has a stable top k.

\subsubsection{Precision}
For the results given by StreamReduce's top-k computation to be meaningful,
it is important for the distribution of the top-k words to be stable, which implies
that task killing minimally impacts the head of the word distribution.
Table~\ref{table:top10} shows the top-10 words and their frequencies. Within the true top-10
words, the first word occurs twice as often as the tenth word, and the difference in frequencies
of adjacently ranked words varies from~400--4000. Given that the data set has approximately~16 million
words and~3500 articles, there are about~4500 words in any given article. Even the most frequently
occuring words only appears on average~8 times per article. Gaps in the hundreds are stable in the
addition or removal of tens of articles.

Figure~\ref{fig:precision} shows that even with a task kill rate of~0.8 and a work level of~0.4,
meaning that the cluster only looks at 8\% of the words in the corpus, the results
are at least~80\% accurate. Increasing the work level, which increases the fidelity of
results emitted by workers, also increases the fidelity of the top~100 results.

@@

\subsubsection{Recall}
Recall is sensitive to the stability of the distribution in the tail. Given that the Wikipedia
data set is long-tailed, the tail of the distribution is very unstable. All of the words
in the bottom-10000 have frequencies in the single digits. Because the distribution in the
tail is so tightly-bunched, recall in the tail of the distribution is most dependent on the
work level of the word count job. Less task killing and higher-fidelity worker computations
benefit recall.

Anything less than perfect computation of a datum leaves out words with a frequency of one.
Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
the same effect on recall as using low fidelity computation routines, so recall decreases as
the task kill rate does. Task killing dominates the impact of work level on recall as
demonstrated by the two lines converging in Figure~\ref{fig:recall}.
